Reading Notes

### 2020-08-17 2pd.tex
more citation fixing

We do not propose a new automated mapping, but instead a way to make the mapping and backmapping process easier for the user.
Simplified Molecular Input Line Entry System or SMILES was designed to represent organic molecules in an unambiguous way (similar to IUPAC) but in a line-entry system which is also readable by a computer\cite{Weininger}.
This makes it a good candidate for specifying a coarse-grain mapping scheme.The open-source package, Openbabel, allows for a SMILES string to be converted to a chemical structure and vice versa.
SMARTS is similar to SMILES but instead of representing a single molecule unambiguously, it has multiple wildcards which can be used for pattern matching.%%<cite openbabel,SMILES, SMARTS>
This pattern matching is also implemented in the Openbabel package.
If we know the SMARTS string for any given CG mapping, we can map the CG site to its center of mass or geometric center.
I have developed a minimum working example of how this can be done and then how the atomistic structure can be recovered.%%<cite grits>
It could be fairly straightforward to implement a lookup to check if bead parameters already exist--say for the MARTINI model-- by going through and writing out the SMARTS pattern for each existing bead type.
An initial headache that could make parameterizing new compounds for the MARTINI method more foolproof.

>>>>

We do not propose a new automated mapping, but instead a way to make the mapping and backmapping process easier for the user.
Simplified Molecular Input Line Entry System or SMILES was designed to represent organic molecules in an unambiguous way (similar to IUPAC) but in a line-entry system which is also readable by a computer\cite{Weininger1988}.
This makes it a good candidate for specifying a coarse-grain mapping scheme.The open-source package, Openbabel, allows for a SMILES string to be converted to a chemical structure and vice versa.
SMARTS is similar to SMILES but instead of representing a single molecule unambiguously, it has multiple wildcards which can be used for pattern matching.%%<cite openbabel,SMILES, SMARTS>
This pattern matching is also implemented in the Openbabel package.
If we know the SMARTS string for any given CG mapping, we can map the CG site to its center of mass or geometric center.
I have developed a minimum working example of how this can be done and then how the atomistic structure can be recovered.%%<cite grits>
It could be fairly straightforward to implement a lookup to check if bead parameters already exist--say for the MARTINI model-- by going through and writing out the SMARTS pattern for each existing bead type.
An initial headache that could make parameterizing new compounds for the MARTINI method more foolproof.
